A numerical study of fixation probabilities for strategies in the Iterated Prisoner's Dilemma

### 2017-04-23 tex/main.tex
Update results.

Tables~\ref{tbl:linear_coeficients_std} and~\ref{tbl:linear_coeficients_noisy}
show the coefficients and \(R^2\) value of the linear model relating the rank in
a particular sized population to the ranks in other populations sizes.
% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
% does show that the coefficient of the N=2 column is always low whereas the
% coefficient of the N=14 column is high even in the N=4 row. So how well you do
% in  a match (N=2) has got very little to do with an evolutionary process.

>>>>

Tables~\ref{tbl:linear_coeficients_invasion},~\ref{tbl:linear_coeficients_resistance}
and~\ref{tbl:linear_coeficients_coexist} show the coefficients and \(R^2\) value
of the linear model relating the rank in a particular sized population to the
ranks in other populations sizes.
% TODO Discuss these tables: show that none of the models are great (R^2) BUT it
% does show that the coefficient of the N=2 column is always low whereas the
% coefficient of the N=14 column is high even in the N=4 row. So how well you do
% in  a match (N=2) has got very little to do with an evolutionary process.
